A Practical Optional Type System for Clojure

### 2012-12-06 dissertation/paper.tex
Fix ref sorting. Adjust listings to not break pages
Typos

\usepackage{mmm}
\usepackage{mathpartir}
\usepackage{clj-grammar}
\usepackage{url}
\usepackage[style=alphabetic]{biblatex}
\addbibresource{bibliography.bib}

@@

Dynamic programming languages often abandon the advantages of static type checking 
in favour of their characteristic convenience and flexibility.
Static type checking eliminates many common user errors at compile-time that
are otherwise unnoticed, or are caught later in languages without static type checking.
A recent trend is to aim to combine the advantages of both kinds of languages by adding \emph{optional} static 
type systems to languages without static type checking, while preserving the languages idioms and style.

@@

I am grateful to Sam Tobin-Hochstadt for his pioneering work in this area of research.
He has always been happy to offer assistance and advise throughout this project, which always proved invaluable.

>>>>

\usepackage{mmm}
\usepackage{mathpartir}
\usepackage{clj-grammar}
\usepackage{url}
\usepackage[style=alphabetic, sorting=nyt]{biblatex}
\addbibresource{bibliography.bib}

@@

Dynamic programming languages often abandon the advantages of static type checking 
in favour of their characteristic convenience and flexibility.
Static type checking eliminates many common user errors at compile-time that
are otherwise unnoticed, or are caught later in languages without static type checking.
A recent trend is to aim to combine the advantages of both kinds of languages by adding \emph{optional} static 
type systems to languages without static type checking, while preserving the idioms and style of the language.

@@

I am grateful to Sam Tobin-Hochstadt for his excellent work in this area of research.
He has always been happy to offer assistance and advice throughout this project, which has proved invaluable.
